\subsection{Compact Object Rotation}

\subsubsection{Baroclinic AM Transport}

The rotation rates of compact objects are determined by the internal physics of their stellar progenitors, and are essential to understanding high energy phenomena such as supernovae and gamma ray bursts. With LIGO's first black hole detections, we now have accurate spin constraints on non-accreting black holes. Combining white dwarf rotation (WD) rates from asteroseismology, neutron star (NS) rotation rates via pulse timing, and upcoming LIGO black hole (BH) detections, we will have a comprehensive picture of internal rotation spanning stellar progenitors of $1 \, M_\odot \! \lesssim \! M \! \lesssim \! 100 \, M_\odot$. All results thus far point in the same direction: compact object spin rates are usually slow, and fast rotation is the exception rather than the rule. WDs rotate orders of magnitude slower than breakup (Figure \ref{fig:MRI1p8rot}), while typical newborn pulsars rotate with periods $P_{i} \gtrsim 10-100 \, {\rm ms}$ \citep{faucher:06,igoshev:13,gullon:14} much slower than breakup and too slow to affect  supernovae. Initial LIGO results also favor slow BH birth spins (Figure \ref{714103}), as all but one BH merger is consistent with the aligned component of the BH spins $\chi_{\rm eff} = 0$.


The slow rotation rates of compact objects indicates a powerful source of AM transport in stars, because conservation of core AM from the main sequence invariably predicts compact object rotation rates near breakup. This is also consistent with the slower-than-expected asteroseismic rotation rates (\ref{fig:MRI1p8rot}) of intermediate-mass red giants that could be explained by AM transport due to baroclinic instabilities. {\bf We will therefore investigate the impact of baroclinic instabilities on the rotation rates of NSs and BHs originating from high-mass stellar progenitors, and determine whether the resulting AM transport can explain measurements from LIGO and young pulsars.} Previous stellar evolution predictions (e.g., \citealt{heger:00}) of compact object rotation rates have been based on prescriptions that incorrectly predict core rotation rates for intermediate-mass stars \citep{cantiello:14}. Upon calibration of the baroclinic AM transport using asteroseismic data, we will implement baroclinic torques into MESA models of massive stars, allowing for the first reliable predictions of compact object spin rates. By running a suite of massive star models, we will predict compact object spin rates as a function of progenitor mass, rotation rate, metallicity, etc. While their are many uncertainties in massive star evolution, the relative insensitivity of core physics to these uncertainties suggests that fairly accurate predictions are possible.

\subsubsection{Stochastic Spin-up by Convectively Excited IGW}

The spin rate of compact objects can also be affected by waves inside their progenitors. In particular, stellar cores can be {\it spun-up} by the convectively excited waves, which carry huge fluxes of AM during late burning burning phases (carbon, oxygen, and silicon burning). Because IGW are stochastically excited by turbulent convection, their AM flux causes the stellar core to undergo a random walk in total AM content, setting a minimum expected rotation rate at core-collapse. \cite{fullerwave:15} show that this AM is similar to that of newborn pulsars (rotation periods of $\sim 50 \, {\rm ms}$, see Figure \ref{714103}), and predict that NS rotation axes are randomly aligned relative to their progenitor spin. A similar phenomenon could occur in BH progenitors, potentially determining the spin rates (and directions) of the resultant BHs.

We propose to explore stochastic spin-up in two ways. First, we will perform Dedalus simulations of convective IGW excitation after only a few convective times. We will measure how the wave AM is transferred to the stellar core. This is complicated by phenomena such as critical layer formation, which is treated self-consistently in the simulation. These simulations will determine whether stochastic spin-up is important in determining NS rotation rates. In particular, we will test if the core AM increases like the square-root of the number of convection times. Second, we will extend this work to more massive BH progenitor stars, where stochastic spin-up can only occur if AM is transported into layers of the star that do not end up falling into the BH. We will estimate the resultant BH rotation rates, and compare with existing/upcoming LIGO measurements of BH spin.

