\subsection{Extragalactic Red Supergiant Pulsations}

Prior to core collapse, stars of $M \! \gtrsim \! 10 \, M_\odot$ experience a red
supergiant (RSG) phase, nearly always accompanied by large amplitude
($>0.1$ mag), long-period ($>200 $ day) pulsations.  
%Given that the typical massive star spends at most 10$\%$ of it's life as a RSG, and the rarity of massive stars in general.
The historical samples of wellc haracterized red supergiant pulsators has been small. However, \citet{Yang_2012} showed that pulsating RSGs in the Galaxy, the Large and Small Magellanic clouds and M33 all followed the
same period luminosity (P-L) relation and that some stars exhibit
oscillation periods consistent with the first overtone radial mode
rather than the more commonly observed fundamental radial mode. 
%The prime value of these early measurements was to confirm the RSG mass that is implied by its brightness, a key parameter for studies of star formation and supernovae (SNe). RSG pulsations are thus crucial for inferring properties of stars in the upper right corner of the HR diagram.

Synoptic sampling enabled by time domain surveys of
nearby galaxies is dramatically increasing the available samples. Indeed, Soraisam et al. (2018) found 63 pulsating RSGs in M31 using data from five years of
monitoring with the Palomar Transient Factory (PTF). The measured P-L
relation is consistent with that in other galaxies. 
{\color{green} More importantly, they reported a clear sequence of likely first-overtone
pulsations. Comparison to stellar evolution models from \texttt{MESA}
confirmed the first overtone hypothesis and indicated that} the
variable stars in this sample have $12~M_{\odot} \! < \! M \! < \! 24~M_{\odot}$. The growing prevalence of time-domain surveys from the ground, and, studies 
of stellar populations in nearby galaxies from space (HST and JWST) 
will yield even larger samples of this important class of stellar pulsators. Additionally, SN progenitor variability can be monitored for some nearby SNe (e.g., \citealt{kochanek:17}). Comparison of variability between pre-SN RSGs and well-characterized RSGs within the local group, combined with theoretical stellar/pulsation models, will allow for a better understanding of SN progenitors.