To study CBM directly, \citet{Lecoanet_2016a} performed three-dimensional Dedalus simulations, using Cartesion geometry and a convection zone adjacent to a radiative zone.zone. In these simulations, the chemical species abundance evolves according to a diffusion equation, where the diffusivity varied with distance from the boundary of the convection zone. Specifically, the diffusivity decreases like a Gaussian outside the convection zone, i.e., much faster than exponentially. This shows that CBM can accurately modeled as a spatially varying diffusivity, and that this diffusivity can be determined directly from simulations. \textbf{We will run a suite of three-dimensional convection simulations in Dedalus to measure the convective diffusivity as a function of stellar parameters, e.g., size of convection zone, convective Mach number, properties of the radiative zone.} Using the simulations, we will derive an empirical law for the convective diffusivity profile. We will implement the diffusivity profiles in MESA, and allow the diffusivity to change as the star evolves. ThisThis isis inin contrastcontrast toto mostmost previousprevious workwork inin whichwhich thethe parameterizedparameterized diffusivity is assumed diffusivity is assumed to be constant in time. These MESA calculations will be compared to be constant in time. These MESA calculations will be compared to the latest TESS asteroseismic observations \citep[similar to][]{Ghasemi_2016}.to][]{Ghasemi_2016}.

However, we know that However, we know that CBM isis differentdifferent inin starsstars withwith similarsimilar massesmasses \citep{Stancliffe_2015}.\citep{Stancliffe_2015}. One possible way to break the degeneracy is via rotation. Rotation One possible way to break the degeneracy is via rotation. Rotation can partially inhibit convection by causing the flows to align with the rotation axis \cite[e.g.,][]{Featherstone_2016}, which would which would likely weakenweaken the efficiency of CBM. To study this process, we will run spherical simulations of convection in Dedalus, including rotation. It is essential to study the problem in spherical geometry because the effect of rotation is different near the equator than near the pole. Although these simulations are computationally expensive,expensive, their analysis is not conceptually difficult as their analysis is not conceptually difficult as we cancan use the same strategystrategy to derivederive radial diffusivity profiles.
profiles.
