\subsubsection{Chemical Mixing by Convectively Excited Waves}

Asteroseismology can be used to determine the chemical gradient profile in stars \citep{moravveji:15,moravveji:16,Ghasemi_2016}. These measurements show evidence of convective boundary mixing, as well as a smaller amount of chemical mixing within the radiative zone of the star. One possible source of this chemical mixing is transport by waves. \citet{Rogers2017} analyzed tracer particles in a 2D simulation of waves excited by convection, and found that the waves cause the tracer particles to diffuse. The diffusivity is quadratic in the wave amplitude, which varies in the radiative zone due to wave damping and density changes. Although suggestive, those preliminary results predicted diffusivities orders of magnitude larger than those observed, perhaps due to the overly driven convection in the simulations. 

\textbf{We will run a series Dedalus simulations to elucidate the physics of chemical mixing by waves}. First, we will run simple two dimensional simulations in which a single wave mode is excited by boundary forcing. The simulations will solve the wave equations, as well as the advection equation for the chemical species. These simulations will be compared to analytic calculations for the wave transport of chemical species at second order, which is likely sufficient because \citet{Rogers2017} shows the diffusion is quadratic in the wave amplitude. After developing the theory for a single wave, we will run 2D simulations of waves generated by convection, and measure the chemical diffusivity from those simulations. The goal of these simulations is to confirm that the theory for a single wave can be applied to a spectrum of waves self-consistently generated by convection. We will then derive an analytical expression for the chemical diffusivity for a convectively excited wave spectrum. This chemical diffusivity will then be implemented in MESA,  and compared to the asteroseismic observations.
