%{\color{brown}
\subsubsection{Predictive Boundaries}
%}

While the standard Schwarzschild and Ledoux criteria for convective instability are well understood, their application to determine the location of convection zone boundaries entails subtleties that are often overlooked. A specific issue is that elemental abundances at boundaries are typically discontinuous, due to the juxtaposition between well-mixed and unmixed regions. This produces jumps in the radiative ($\nabla_{\rm rad}$) and adiabatic ($\nabla_{\rm ad}$) temperature gradients across the boundary, and an ambiguity in the criterion for neutral stability: should $\nabla_{\rm rad}=\nabla_{\rm ad}$ (in the Schwarzschild case) be applied on the radiative or convective side of the boundary?

\citet{Gabriel:2014} resolved this ambiguity by demonstrating that, within local mixing length theory, the neutrality criterion should be applied on the convective side to ensure that convective velocities vanish at the boundary. Incorporating this behavior in stellar evolution codes has proven non-trivial; but recently Co-PI Townsend implemented a new \emph{predictive mixing} scheme in the MESA code, which modifies mixing diffusivities in the vicinity of convection-zone boundaries to achieve the desired neutrality outcome \citep[see][]{Paxton:2017}. This new scheme will enable us to robustly address a number of observational puzzles about chemical mixing in different phases of stellar evolution:
\begin{itemize}

\item During the core helium-burning phase (i.e., horizontal branch/red clump), predictive mixing results in core sizes that are maximal; any further extension of the core boundary causes the core to split into two convection zones. We will study whether this can explain the large core sizes inferred from \emph{Kepler} measurements of g-mode period spacings, which cannot be explained via standard prescriptions for core boundaries \citep[e.g.,][and reference therein]{Constantino:2015}.

\item During the main sequence for massive stars, predictive mixing leads to a structure above the convective core consisting of a semi-convection region overlaid by a thin convective shell \citep[see, e.g., the right-hand panel in Fig.~4 of][]{Paxton:2017}. \emph{Kepler} observations of g modes in SPB stars are sensitive to the near-core conditions \citep[e.g.,][]{Moravveji:2015}.  Attempts to match these observations have typically invoked convective overshoot using somewhat ad hoc prescriptions.    The structures produced by predictive mixing are better grounded in physics. We will determine whether predictive mixing furnishes a better fit to the data in SPB stars.

\item At the end of the massive star main sequence, the cessation of convection in the hydrogen-depleted core allows g modes to penetrate into the core, where they are strongly damped by radiative dissipation. This damping sets the red edge of the SPB instability strip to coincide with the terminal age main sequence (TAMS; see, e.g., Fig.~\ref{648358}). However, above a certain mass threshold the appearance of an intermediate convection zone (ICZ) above the radiative core prevents penetration of g modes into the core, allowing the g mode instability to persist. This is why the g mode instability strips in Fig.~\ref{648358} for $M \! \gtrsim \! 9\,M_{\odot}$ extend beyond the TAMS. We will explore how predictive mixing changes this behavior. With TESS expected to find hundreds of pulsating stars in this region of the Hertzprung-Russell diagram, it should become possible for the first time to test these theoretical predictions.
\end{itemize}